Human capital mediates natural selection in contemporary humans

### 2022-05-03 why-natural-selection.Rmd

  confint_geom_segment <- if (conf_int) confint_geom_segment() else NULL

  dfr %>% mutate(
          !! score_col := pretty_names(!! score_col),
          !! score_col := fct_reorder(!! score_col, estimate, order_abs(order_idx))
        ) %>% 
        rename(p = p.value) %>% 
        ggplot(aes(estimate, {{score_col}}, yend = {{score_col}}, 
                     fill = {{fill_col}}, ..., colour = p < 0.05/{{n_regs}})) +
          my_vline + 
          confint_geom_segment +
          pval_geom_point(fill = if(rlang::quo_is_null(fill_col)) "steelblue") +
          pval_scale() +
          my_fill_scale(n = n_cats, direction = fill_direction) +
          my_labs() +
          my_theme() +
          scale_linetype_manual(name = "", values = c("95% c.i. uncorrected" = 1))

}

>>>>

  dfr %>% mutate(
    !! score_col := pretty_names(!! score_col),
    !! score_col := fct_reorder(!! score_col, estimate, order_abs(order_idx))
  ) %>% 
    rename(p = p.value) %>% 
    ggplot(aes(estimate, {{score_col}}, yend = {{score_col}}, 
               shape = {{fill_col}}, ...)) +
    my_vline + 
    confint_geom_segment +
    geom_point(size = 1.8, aes(color = {{fill_col}})) +
    geom_point(size = 0.7, color = "white", aes(alpha = p < 0.05/33)) +
    my_fill_scale(aesthetics = "color", n = n_cats, direction = fill_direction) +
    scale_shape_manual(values = 1:n_cats + 14) +
    my_labs() +
    my_theme() +
    scale_linetype_manual(name = "", values = c("95% c.i." = 1)) +
    scale_alpha_discrete(range = c(1, 0),
                         guide = guide_legend(
                           override.aes = list(
                             shape = c(1, 16),
                             color = "black",
                             alpha = 1,
                             size = 1.8
                           )
                         ))
}
